---
title: "Mini-Project 1"
author: "Michael Ulis, Ayla Orona, Maeric Barrows"
date: "2024-03-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Front Matter
```{r}
remove(list = ls())

#Add libraries as needed
library(tidyverse)
library(readxl)
<<<<<<< HEAD

#Read in dataset
COD <- read_excel("CODGames2_mp.xlsx")
View(COD)
```
```{r}
remove(list = ls())

#Add libraries as needed
library(tidyverse)
library(readxl)

#Read in dataset
COD <- read_excel("C:/Users/aylao/Downloads/CODGames2_mp.xlsx")
View(COD)
```


## Elimination Summary
```{r}
sum(is.na(COD$Eliminations))
```

```{r}

COD %>%
  summarize(N = n(),
            mean = mean(Eliminations),
            median= median(Eliminations),
            StandardD = sd(Eliminations),
            min = min(Eliminations),
            max = max(Eliminations))

```
The Eliminations variable is quantitative. The amount of missing data Eliminations has is 0 because you are guaranteed to get eliminated per game. The mean of Eliminations is 15.09005, the median is 14, the Standard Deviation is 6.133161, the minimum is 2, and the max is 39.

```{r}
ggplot(data = COD, mapping = aes(x = Eliminations))+
  geom_histogram(color = "black", fill = "#880808")
```

## Total XP Summary
```{r}
sum(is.na(COD$TotalXP))
```
```{r}
COD %>%
  summarize(N = n(),
            mean = mean(TotalXP),
            median = median(TotalXP),
            StandardD = sd(TotalXP),
            min = min(TotalXP),
            max = max(TotalXP))
```
The number of missing data for TotalXP is 0. The mean for TotalXP is 11975.4, the median is 10328, the standard deviation is 6166.652, the minimum TotalXP is 1935, and the max is 43816.

```{r}
ggplot(data = COD, mapping = aes(x = TotalXP))+
  geom_histogram(color = "black", fill = "#880808")
```



=======
```

```{r}
#Read in dataset
library(readxl)
COD <- read_excel("C:/Misha/College Stuff/cmpsc132/hw/CODGames2_mp.xlsx")
glimpse(COD)
```
Choice

```{r}
choice_table <- COD %>%
  group_by(Choice) %>%
  summarise(N = n()) %>%
  arrange(desc(N))

choice_table
```

```{r}
ggplot(data = COD, mapping = aes(x = Choice)) +
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

Eliminations

Deaths

Score

```{r}
score_table <- COD %>%
  summarise(total_score = sum(Score, na.rm = TRUE),
            mean_score = mean(Score, na.rm = TRUE),
            median_score = median(Score, na.rm = TRUE),
            sd_score = sd(Score, na.rm = TRUE),
            min_score = min(Score, na.rm = TRUE),
            max_score = max(Score, na.rm = TRUE))

score_table
```

```{r}
ggplot(data = COD, mapping = aes(x = Choice, y = Score)) + 
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

Total XP

Primary Weapon
>>>>>>> 92ac87ed808e98a09658a1b893fa65d49af3e5b0

